---
title: "Store 24(A)"
author: "Parv Patni"
date: "December 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
store <- read.csv(paste("Store24.csv", sep=""))
head(store)
summary(store)
```
mean and standards deviations of Profit
```{r}
mean(store$Profit)
sd(store$Profit)
```
mean and standard deviation of MTenure.
```{r}
mean(store$MTenure)
sd(store$MTenure)
```
mean and standard deviation of CTenure.
```{r}
mean(store$CTenure)
sd(store$CTenure)
```
Top 10 most profitable stores.
```{r}
attach(store)
exhib1 <- store[order(-Profit),]
exhib1[1:10,1:5]
```
Top 10 least profitable stores
```{r}
exhib1 <- store[order(Profit),]
exhib1[1:10,1:5]
```
Plot of Profit vs MTenure
```{r}
plot(MTenure,Profit)
```
Plot of Profit vs CTenure
```{r}
plot(CTenure,Profit)
```

```{r}
library(corrplot)
corrplot(corr=cor(store[ , c(1:14)], use="complete.obs"), 
         method ="ellipse")
```
MTenure
```{r}
cor(store$Profit,store$MTenure)
```
Correlation between Profit and CTenure
```{r}
cor(store$Profit,store$CTenure)
```
Corrgram of all the variables
```{r}
library(corrgram)
corrgram(store, order=TRUE,
         main="Corrgram of all the Variables",
         lower.panel=panel.shade, upper.panel=panel.pie,
         diag.panel=panel.minmax, text.panel=panel.txt) 
```
The p - Value is 8.193e-05.

Correlation test between Profit and CTenure
```{r}
cor.test(store$Profit,store$CTenure)
```
The p - Value is 0.02562.

Regression of Profit on {MTenure, CTenure, Comp, Pop, PedCount, Res, Hours24, Visibility}
```{r}
regr <- lm(Profit ~ MTenure + CTenure + Comp + Pop + PedCount + Res + Hours24 + Visibility, data = store)
summary(regr)
```
```{r}
regr$coefficients
residuals(regr)
```


##Summary

1.Profit has the strongest correlation with crew tenure and with manager tenure.

2.Crew skill is directly dependent on the crew tenure, meaning crew retention will lead to increase in skills, which inturn leads to higher profits.

3.The most profitable store is with ID:74 and the least profitable store is :57

4.Profit also has a significantly strong relationship with population served by the store, pedestrian traffic rate and crew skill.It also has a negative correlation with competition and resedential area. 

5.stores located in industrial areas generally have a high employee retention and skill rate. Hence, any employee retention programme must primarily be focused in stores located in resedential areas.

6.Coming to the regression part,the p-value of the model is statistically significant.It means it is a good fit model.

7.R square value is:0.6379.It means that 63.79% of variations in the dependent variable is explained by the independent variable.

8.Adjusted R square value is 0.594.It means 59.4% variation in the dependent variable is explained by the independent variable.This values decreases as we add no of independent variables.

9.Variables MTenure, Comp, PedCount, Hours24, CTenure, Pop, Res are Statistically significant with p<0.05.

10.Variable Visibility is statistically insignificant with p>0.05.